TimeVaryingDetection_mrmr

### 2024-11-13 code/R/TimeVaryingDetection_mrmr.Rmd
document formatting updates

**Here, I make a custom version of mrmr functons, aiming to get time-varying detection probability estimates. I updated the twostate.stan model to this end, and am now customizing mrmr's fit_model() function to use my updated stan model**

@@

library(cmdstanr)
library(mrmr)

**Write custom version of mrmr::fit_model()**

Change only line 53. Tell function to pull from my TVD_twostate.stan file

# Custom fit function using the updated Stan model file
fit_model_custom <- function(
  data,
  seed = NULL,
  refresh = NULL,
  init = NULL,
  save_latent_dynamics = FALSE,
  output_dir = NULL,
  output_basename = NULL,
  sig_figs = NULL,
  chains = 4,
  parallel_chains = getOption("mc.cores", 1),
  chain_ids = seq_len(chains),
  threads_per_chain = NULL,
  opencl_ids = NULL,
  iter_warmup = 1000,
  iter_sampling = 1000,
  save_warmup = FALSE,
  thin = NULL,
  max_treedepth = NULL,
  adapt_engaged = TRUE,
  adapt_delta = NULL,
  step_size = NULL,
  metric = NULL,
  metric_file = NULL,
  inv_metric = NULL,
  init_buffer = NULL,
  term_buffer = NULL,
  window = NULL,
  fixed_param = FALSE,
  show_messages = TRUE,
  compile = TRUE,
  ...
) {
  # updated to use my custom stan model
  stan_file <- "updated_twostate.stan" # specify new path

>>>>

# Custom version of MLRG's mrmr package for mark-recapture data analysis

-   fit_model_custom() is a copy of mrmr's fit_model() function, changed only to call on a modified version of the underlying stan model.

    The modified stan model...

    -   allows for independent session-varying estimates of frog detection probabilities
    -   includes more parameter estimates in the generated quantities block
        -   p (detection probability, varying by session)
        -   phi_est (phi, or survival probability, estimated for the whole population between primary periods)

**Load packages**

```{r}
library(cmdstanr)
library(mrmr)
```

**Custom version of mrmr::fit_model()**

@@

# Custom fit function using the updated Stan model file
fit_model_custom <- function(
  data,
  seed = NULL,
  refresh = NULL,
  init = NULL,
  save_latent_dynamics = FALSE,
  output_dir = NULL,
  output_basename = NULL,
  sig_figs = NULL,
  chains = 4,
  parallel_chains = getOption("mc.cores", 1),
  chain_ids = seq_len(chains),
  threads_per_chain = NULL,
  opencl_ids = NULL,
  iter_warmup = 1000,
  iter_sampling = 1000,
  save_warmup = FALSE,
  thin = NULL,
  max_treedepth = NULL,
  adapt_engaged = TRUE,
  adapt_delta = NULL,
  step_size = NULL,
  metric = NULL,
  metric_file = NULL,
  inv_metric = NULL,
  init_buffer = NULL,
  term_buffer = NULL,
  window = NULL,
  fixed_param = FALSE,
  show_messages = TRUE,
  compile = TRUE,
  ...
) {
  # updated to use my custom stan model
  stan_file <- "JI_custom_twostate.stan" # specify local path
